TODO

### 2021-03-10 publications/The_tool_intro/paper.tex
tool_intro:P4 example

\begin{table*}
\begin{tabular}{|p{8.4cm}|p{8.4cm}|}
\hline
\begin{lstlisting}[basicstyle=\scriptsize]
header ethernet_t {
    macAddr_t dstAddr;
    macAddr_t srcAddr;
    bit<16>   etherType; }

@@

parser MyParser(...) {
    state start { transition parse_ethernet; }
    state parse_ethernet {
        packet.extract(hdr.ethernet);
        transition select(hdr.ethernet.etherType) {
            TYPE_IPV4: parse_ipv4;
            default: accept; } }
    state parse_ipv4 {
        packet.extract(hdr.ipv4);
        transition accept; } }
\end{lstlisting}
&
\begin{lstlisting}[basicstyle=\scriptsize]
control MyIngress(...) {
   apply {
        if (hdr.ipv4.isValid()) {
            ipv4_lpm.apply(); }
   }         
   action drop() {
        mark_to_drop(standard_metadata);
    }    
    action ipv4_forward(macAddr_t dstAddr, egressSpec_t port) {
        standard_metadata.egress_spec = port;
        hdr.ethernet.srcAddr = hdr.ethernet.dstAddr;
        hdr.ethernet.dstAddr = dstAddr;
        hdr.ipv4.ttl = hdr.ipv4.ttl - 1;
    }    
    table ipv4_lpm {
        key = {  hdr.ipv4.dstAddr: lpm;  }
        actions = {
            ipv4_forward;
            drop;
            NoAction;}
        ... }   
}
control MyDeparser(packet_out packet, in headers hdr) {
    apply {
        packet.emit(hdr.ethernet);
        packet.emit(hdr.ipv4);}
}
\end{lstlisting}\\
\hline
\end{tabular}
\caption{P4 example}
  \label{code:P4}
\end{table*}

>>>>

\begin{table*}
\begin{tabular}{|p{3.3cm}|p{5.9cm}|p{7.7cm}|}
\hline
\begin{lstlisting}[basicstyle=\scriptsize]
header ethernet_t {
  macAddr_t dstAddr;
  macAddr_t srcAddr;
  bit<16>   etherType; }

@@

\end{lstlisting}
&
\begin{lstlisting}[basicstyle=\scriptsize]
parser MyParser(...) {
  state start { transition parse_ethernet; }
  state parse_ethernet {
    packet.extract(hdr.ethernet);
    transition select(hdr.ethernet.etherType) {
      TYPE_IPV4: parse_ipv4;
      default: accept; } }
  state parse_ipv4 {
    packet.extract(hdr.ipv4);
    transition accept; } }
control MyIngress(...) {
  apply {
    if (hdr.ipv4.isValid()) {
           ipv4_lpm.apply(); }
  }         
  action drop() {
    mark_to_drop(standard_metadata);
  }    
\end{lstlisting}
&
\begin{lstlisting}[basicstyle=\scriptsize]
  action ipv4_forward(macAddr_t dstAddr, egressSpec_t port) {
    standard_metadata.egress_spec = port;
    hdr.ethernet.srcAddr = hdr.ethernet.dstAddr;
    hdr.ethernet.dstAddr = dstAddr;
    hdr.ipv4.ttl = hdr.ipv4.ttl - 1;
  }    
  table ipv4_lpm {
    key = {  hdr.ipv4.dstAddr: lpm;  }
    actions = {
      ipv4_forward;
      drop;
      NoAction;}
    ... }   
}
control MyDeparser(packet_out packet, in headers hdr) {
  apply {
    packet.emit(hdr.ethernet);
    packet.emit(hdr.ipv4);}
}
\end{lstlisting}\\
\hline
\end{tabular}
\caption{P4 example}
  \label{code:P4}
\end{table*}
